---
title: "Study 1 Analysis"
output:   
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    theme: united
---

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', eval=TRUE}

library(psych)
library(ggplot2)
library(tidyverse)
library(effects)
## Library for the multiple comparisons
library(phia)
## Library to compute the effect sizes
library(sjstats)
library(lsr)
library(lavaan)
library(ggthemes)
library(tibble)
library(car)
library(olsrr)
library(pwr)

library(R2jags)
library(rjags)
library(runjags)
library("lattice")
library("superdiag")
library(gtools)

library(bayestestR) 
library("ggmcmc")
library(brms)
library(BayesFactor)
library(MCMCvis)

source('Useful Code V2.R')

library(readr)
attobo <- read_csv("attobo1_clean.csv")

colnames(attobo) <- tolower(colnames(attobo))

attobo$scenario <- as.factor(attobo$scenario)

attobo$attribution <- attobo$scenario

attobo$attribution_effort <- factor(attobo$attribution, levels = c("Effort", "Strategy", "Aptitude"))
attobo$attribution_strat <- factor(attobo$attribution, levels = c( "Strategy","Effort", "Aptitude"))

attobo$expectancy <- (attobo$expectancy - 1)/10
attobo$expectancy <- ifelse(attobo$expectancy == 1, .999,
                     ifelse(attobo$expectancy == 0, .001, attobo$expectancy) )


```

# Descriptive Stats

```{r echo=TRUE, warning=FALSE, message=FALSE, eval=TRUE}
## Sample Breakdown
group_by(attobo, attribution) %>%
  summarise(n())
  
## means and sd of DVs
aggregate(cbind(method, bruteforce, seekhelp)~attribution, data=attobo, FUN=mean)

aggregate(cbind(method, bruteforce, seekhelp)~attribution, data=attobo, FUN=sd)

aggregate(cbind(combined_method, notetaking, total, convergent_method)~attribution, data=attobo, FUN=mean)

aggregate(cbind(combined_method, notetaking, total, convergent_method)~attribution, data=attobo, FUN=sd)

## Locus, Variability, and Uncontrollability
attobo %>%
  group_by(attribution) %>%
  summarise(meanLocusOut = mean(locusout, na.rm = T),
            sdLocusOut = sd(locusout, na.rm = T),
            meanVar = mean(variability, na.rm = T),
            sdVar = sd(variability, na.rm = T),
            meanUncon = mean(uncontrollability, na.rm = T),
            sdUncon = sd(uncontrollability, na.rm = T))

attobo.advice <- attobo %>%
  select(method, bruteforce, seekhelp, convergent_method,
         total, expectancy, combined_method, total_method)

attobo.attribution <- attobo %>%
  select(aptout, aptvar, aptuncon, 
         effortout, effortvar, effortuncon,
         stratout, stratvar, stratuncon,
         luckout, luckvar, luckuncon,
         taskout, taskvar, taskuncon,
         moodout, moodvar, mooduncon)

attobo.others <- attobo %>%
  select(expectancy, gender, age, education, sms_mean,
         smo_mean, mp_mean, so_mean)
  

ggplot(data = gather(attobo.advice, factor_key = TRUE), aes(x = factor(value))) +
  geom_bar() + 
  facet_wrap(~ key,scales = "free", as.table = TRUE, nrow = 3) + xlab("") + 
  theme_bw()

ggplot(data = gather(attobo.attribution, factor_key = TRUE), aes(x = factor(value))) +
  geom_bar() + 
  facet_wrap(~ key,scales = "free", as.table = TRUE, nrow = 3) + xlab("") + 
  theme_bw()

ggplot(data = gather(attobo.others, factor_key = TRUE), aes(x = factor(value))) +
  geom_bar() + 
  facet_wrap(~ key,scales = "free", as.table = TRUE, nrow = 3) + xlab("") + 
  theme_bw()


```

###################################################################
# Power Analysis

```{r}

pwr.chisq.test(w = .3, df = 2, sig.level =.05, power = .8)

```

# Frequentist Estimate

```{r}

library(glm2)
library(betareg)

method.freq <- glm2(combined_method ~ attribution_strat, data = attobo, family = poisson(link = "log"))

convergent.freq <- glm2(convergent_method ~ attribution_effort, data = attobo, family = poisson(link = "log"))

bruteforce.freq <- glm2(bruteforce ~ attribution_effort, data = attobo, family = poisson(link = "log"))

expectancy.freq <- betareg(expectancy ~ attribution, data = attobo, link = "logit" )

seekhelp.freq <- glm2(seekhelp ~ attribution, data = attobo, family = poisson(link = "log"))

summary(glm2(combined_method ~ attribution_strat, data = attobo, family = poisson(link = "log")))

summary(glm2(convergent_method ~ attribution_effort, data = attobo, family = poisson(link = "log")))

summary(glm2(bruteforce ~ attribution_effort, data = attobo, family = poisson(link = "log")))

summary(betareg(expectancy ~ attribution, data = attobo, link = "logit" ))

Anova(glm2(combined_method ~ attribution_strat, data = attobo, family = poisson(link = "log")))

Anova(glm2(convergent_method ~ attribution_effort, data = attobo, family = poisson(link = "log")))

Anova(glm2(bruteforce ~ attribution_effort, data = attobo, family = poisson(link = "log")))

Anova(betareg(expectancy ~ attribution, data = attobo, link = "logit" ))

```



###################################################################

# Bayesian Model - method Advice

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}


strategy <- ifelse(attobo$attribution == "Strategy", 1,0)
effort <- ifelse(attobo$attribution == "Effort", 1, 0) 

method <- attobo$method

attobo.datjags <- list(strategy = strategy, effort = effort, method = method, N = nrow(attobo))
attobo.datjags

```

## Model Specification

```{r}

attobo.model <- function() {
  for(i in 1:N){
    # lambda is mean and variance of the poisson distribution
    method[i] ~ dpois(lambda[i])
    log(lambda[i]) <- b[1] + b[2] * effort[i] + b[3] * strategy[i]
  }
  
  #priors
  b[1] ~ dnorm(0, 0.0025)
  b[2] ~ dnorm(0, 0.0025)
  b[3] ~ dnorm(0, 0.0025)
  
  for (i in 1:N){
    
    error[i] <- lambda[i] - method[i]
  
  }
  
  
}

```


```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}

attobo.params <- c("b", "lambda", "error")

attobo.params2 <- c("b")

```

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}

b.inits <- method.freq$coefficients

attobo.inits1 <-  list( "b" = b.inits)
attobo.inits2 <- list( "b" = rep(0, 3) )
attobo.inits3 <- list( "b" = rep(1, 3) )
attobo.inits4 <- list( "b" = rep(-1, 3) )
attobo.inits5 <- list( "b" = rep(2, 3) )
attobo.inits <- list(attobo.inits1, attobo.inits2,attobo.inits3, attobo.inits4,attobo.inits5)

```

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide', eval = FALSE}

set.seed(1128)
attobo.fit <- jags(data = attobo.datjags, inits = attobo.inits, parameters.to.save = attobo.params, 
                n.chains = 5, n.iter = 100000, n.burnin = 10000, model.file = attobo.model)

attobo.fit.upd <- update(attobo.fit, n.iter =1000)
attobo.fit.upd <- autojags(attobo.fit)

set.seed(1128)
attobo.fit.convergence <- jags(data = attobo.datjags, inits = attobo.inits, parameters.to.save = attobo.params2, 
                n.chains = 5, n.iter = 100000, n.burnin = 10000, model.file = attobo.model)

attobo.fit.upd.convergence <- update(attobo.fit.convergence, n.iter =1000)
attobo.fit.upd.convergence <- autojags(attobo.fit.convergence)

```

```{r eval = FALSE}

attobo.fit.mcmc <- as.mcmc(attobo.fit)
#save(attobo.fit.mcmc, file = "attobo.method.RData")

attobo.fit.convergence.mcmc <- as.mcmc(attobo.fit.convergence)
summary(attobo.fit.convergence.mcmc)

```

## Convergence Diagnostics

```{r figure = TRUE, fig.width=6, fig.height=6, fig.align='center'}
                                      
MCMCtrace(attobo.fit.convergence.mcmc, ind = TRUE, pdf = FALSE )

autocorr.plot(attobo.fit.convergence.mcmc[1], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[2], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[3], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[4], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[5], ask = FALSE)
```

```{r}

attobo.out <- as.data.frame(as.matrix(attobo.fit.mcmc))

pred.method <- attobo.out[, grep("lambda[", colnames(attobo.out), fixed = T)]

## saving data
#save(attobo.out, file = "attobo.method.RData")

## estimated count for each participant
pred.method <- pred.method[, c(mixedsort(names(pred.method)))]

strategy.id <- as.numeric(unlist(which(attobo$attribution == "Strategy")))
effort.id <- as.numeric(unlist(which(attobo$attribution == "Effort")))
aptitude.id <- as.numeric(unlist(which(attobo$attribution == "Aptitude")))

pred.method$strategy.sim <- apply(pred.method[, strategy.id], 1, mean)
pred.method$effort.sim <- apply(pred.method[, effort.id], 1, mean)
pred.method$aptitude.sim <- apply(pred.method[, aptitude.id], 1, mean)

quantile(pred.method$strategy.sim, probs = c(.025, .5, .975))
quantile(pred.method$effort.sim, probs = c(.025, .5, .975))
quantile(pred.method$aptitude.sim, probs = c(.025, .5, .975))

pred.method$diff.1 <- pred.method$strategy.sim - pred.method$aptitude.sim
pred.method$diff.2 <- pred.method$strategy.sim - pred.method$effort.sim
pred.method$diff.3 <- pred.method$effort.sim - pred.method$aptitude.sim

quantile(pred.method$diff.1, probs = c(.025, .5, .975))
quantile(pred.method$diff.2, probs = c(.025, .5, .975))
quantile(pred.method$diff.3, probs = c(.025, .5, .975))

```

```{r}

error.method <- attobo.out[, grep("error[", colnames(attobo.out), fixed = T)]
#save(error.method, file = "error.method.RData")

error <- as.vector(unlist(lapply(error.method, mean)))
mean(error)
plot(density(error))

```



## Expected Counts for each attribution

```{r echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
attobo.posterior.coefs <- select(pred.method, `strategy.sim`, `effort.sim`,`aptitude.sim`)
names(attobo.posterior.coefs) <- c("Strategy", "Effort", "Aptitude")

attobo.posterior.coefs.long <- gather(attobo.posterior.coefs)
#head(attobo.posterior.coefs.long)


```

```{r}
library("ggridges")
ggplot(data = attobo.posterior.coefs.long, aes(x = value, y = key)) + 
  stat_density_ridges(quantile_lines = TRUE, 
                      quantiles = c(0.025, 0.5, 0.975), 
                      alpha = 0.7)
```

###############################################################################




# Bayesian Model - bruteforce Advice

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}


strategy <- ifelse(attobo$attribution == "Strategy", 1,0)
effort <- ifelse(attobo$attribution == "Effort", 1, 0) 

bruteforce <- attobo$bruteforce

attobo.datjags <- list(strategy = strategy, effort = effort, bruteforce = bruteforce, N = nrow(attobo))
attobo.datjags

```

## Model Specification

```{r}

attobo.model <- function() {
  for(i in 1:N){
    # lambda is mean and variance of the poisson distribution
    bruteforce[i] ~ dpois(lambda[i])
    log(lambda[i]) <- b[1] + b[2] * effort[i] + b[3] * strategy[i]
  }
  
  #priors
  b[1] ~ dnorm(0, 0.0025)
  b[2] ~ dnorm(0, 0.0025)
  b[3] ~ dnorm(0, 0.0025)
  
  for (i in 1:N){
    
    error[i] <- lambda[i] - bruteforce[i]
  
  }
  
  
}

```


```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}

attobo.params <- c("b", "lambda", "error")

attobo.params2 <- c("b")

```

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}

b.inits <- bruteforce.freq$coefficients

attobo.inits1 <-  list( "b" = b.inits)
attobo.inits2 <- list( "b" = rep(0, 3) )
attobo.inits3 <- list( "b" = rep(1, 3) )
attobo.inits4 <- list( "b" = rep(-1, 3) )
attobo.inits5 <- list( "b" = rep(2, 3) )
attobo.inits <- list(attobo.inits1, attobo.inits2,attobo.inits3, attobo.inits4,attobo.inits5)

```

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide', eval = FALSE}

set.seed(1128)
attobo.fit <- jags(data = attobo.datjags, inits = attobo.inits, parameters.to.save = attobo.params, 
                n.chains = 5, n.iter = 100000, n.burnin = 10000, model.file = attobo.model)

attobo.fit.upd <- update(attobo.fit, n.iter =1000)
attobo.fit.upd <- autojags(attobo.fit)

set.seed(1128)
attobo.fit.convergence <- jags(data = attobo.datjags, inits = attobo.inits, parameters.to.save = attobo.params2, 
                n.chains = 5, n.iter = 100000, n.burnin = 10000, model.file = attobo.model)

attobo.fit.upd.convergence <- update(attobo.fit.convergence, n.iter =1000)
attobo.fit.upd.convergence <- autojags(attobo.fit.convergence)

```

```{r eval = FALSE}

attobo.fit.mcmc <- as.mcmc(attobo.fit)
#save(attobo.fit.mcmc, file = "attobo.bruteforce.RData")

attobo.fit.convergence.mcmc <- as.mcmc(attobo.fit.convergence)
summary(attobo.fit.convergence.mcmc)

```

## Convergence Diagnostics

```{r figure = TRUE, fig.width=6, fig.height=6, fig.align='center'}
                                      
MCMCtrace(attobo.fit.convergence.mcmc, ind = TRUE, pdf = FALSE )

autocorr.plot(attobo.fit.convergence.mcmc[1], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[2], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[3], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[4], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[5], ask = FALSE)
```

```{r}

attobo.out <- as.data.frame(as.matrix(attobo.fit.mcmc))

pred.bruteforce <- attobo.out[, grep("lambda[", colnames(attobo.out), fixed = T)]

## saving data
#save(attobo.out, file = "attobo.bruteforce.RData")

## estimated count for each participant
pred.bruteforce <- pred.bruteforce[, c(mixedsort(names(pred.bruteforce)))]

strategy.id <- as.numeric(unlist(which(attobo$attribution == "Strategy")))
effort.id <- as.numeric(unlist(which(attobo$attribution == "Effort")))
aptitude.id <- as.numeric(unlist(which(attobo$attribution == "Aptitude")))

pred.bruteforce$strategy.sim <- apply(pred.bruteforce[, strategy.id], 1, mean)
pred.bruteforce$effort.sim <- apply(pred.bruteforce[, effort.id], 1, mean)
pred.bruteforce$aptitude.sim <- apply(pred.bruteforce[, aptitude.id], 1, mean)

quantile(pred.bruteforce$strategy.sim, probs = c(.025, .5, .975))
quantile(pred.bruteforce$effort.sim, probs = c(.025, .5, .975))
quantile(pred.bruteforce$aptitude.sim, probs = c(.025, .5, .975))


```

```{r}

error.bruteforce <- attobo.out[, grep("error[", colnames(attobo.out), fixed = T)]
#save(error.bruteforce, file = "error.bruteforce.RData")

error <- as.vector(unlist(lapply(error.bruteforce, mean)))
mean(error)
plot(density(error))

```



## Expected Counts for each attribution

```{r echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
attobo.posterior.coefs <- select(pred.bruteforce, `strategy.sim`, `effort.sim`,`aptitude.sim`)
names(attobo.posterior.coefs) <- c("Strategy", "Effort", "Aptitude")

attobo.posterior.coefs.long <- gather(attobo.posterior.coefs)
#head(attobo.posterior.coefs.long)


```

```{r}
library("ggridges")
ggplot(data = attobo.posterior.coefs.long, aes(x = value, y = key)) + 
  stat_density_ridges(quantile_lines = TRUE, 
                      quantiles = c(0.025, 0.5, 0.975), 
                      alpha = 0.7)
```


```{r}
attobo.posterior.coefs.sum <- summarize(group_by(attobo.posterior.coefs.long, key),
                                        median_coef = median(value),
                                        lower_coef = quantile(value, probs = c(0.025)),
                                        upper_coef = quantile(value, probs = c(0.975)))

bruteforce.summary <- attobo.posterior.coefs.sum
```

###############################################################################

# Bayesian Model - mandatory Advice

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}


strategy <- ifelse(attobo$attribution == "Strategy", 1,0)
effort <- ifelse(attobo$attribution == "Effort", 1, 0) 

convergent <- attobo$convergent_method

attobo.datjags <- list(strategy = strategy, effort = effort, convergent = convergent, N = nrow(attobo))
attobo.datjags

```

## Model Specification

```{r}

attobo.model <- function() {
  for(i in 1:N){
    # lambda is mean and variance of the poisson distribution
    convergent[i] ~ dpois(lambda[i])
    log(lambda[i]) <- b[1] + b[2] * effort[i] + b[3] * strategy[i]
  }
  
  #priors
  b[1] ~ dnorm(0, 0.0025)
  b[2] ~ dnorm(0, 0.0025)
  b[3] ~ dnorm(0, 0.0025)
  
  for (i in 1:N){
    
    error[i] <- lambda[i] - convergent[i]
  
  }
  
  
}

```


```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}

attobo.params <- c("b", "lambda", "error")

attobo.params2 <- c("b")

```

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}

b.inits <- convergent.freq$coefficients

attobo.inits1 <-  list( "b" = b.inits)
attobo.inits2 <- list( "b" = rep(0, 3) )
attobo.inits3 <- list( "b" = rep(1, 3) )
attobo.inits4 <- list( "b" = rep(-1, 3) )
attobo.inits5 <- list( "b" = rep(2, 3) )
attobo.inits <- list(attobo.inits1, attobo.inits2,attobo.inits3, attobo.inits4,attobo.inits5)

```

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide', eval = FALSE}

set.seed(1128)
attobo.fit <- jags(data = attobo.datjags, inits = attobo.inits, parameters.to.save = attobo.params, 
                n.chains = 5, n.iter = 100000, n.burnin = 10000, model.file = attobo.model)

attobo.fit.upd <- update(attobo.fit, n.iter =1000)
attobo.fit.upd <- autojags(attobo.fit)

set.seed(1128)
attobo.fit.convergence <- jags(data = attobo.datjags, inits = attobo.inits, parameters.to.save = attobo.params2, 
                n.chains = 5, n.iter = 100000, n.burnin = 10000, model.file = attobo.model)

attobo.fit.upd.convergence <- update(attobo.fit.convergence, n.iter =1000)
attobo.fit.upd.convergence <- autojags(attobo.fit.convergence)

```

```{r eval = FALSE}

attobo.fit.mcmc <- as.mcmc(attobo.fit)
#save(attobo.fit.mcmc, file = "attobo.convergent.RData")

attobo.fit.convergence.mcmc <- as.mcmc(attobo.fit.convergence)
summary(attobo.fit.convergence.mcmc)

```

## Convergence Diagnostics

```{r figure = TRUE, fig.width=6, fig.height=6, fig.align='center'}
                                      
MCMCtrace(attobo.fit.convergence.mcmc, ind = TRUE, pdf = FALSE )

autocorr.plot(attobo.fit.convergence.mcmc[1], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[2], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[3], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[4], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[5], ask = FALSE)
```

```{r}


attobo.out <- as.data.frame(as.matrix(attobo.fit.mcmc))

pred.convergent <- attobo.out[, grep("lambda[", colnames(attobo.out), fixed = T)]

## saving data
#save(attobo.out, file = "attobo.convergent.RData")

## estimated count for each participant
pred.convergent <- pred.convergent[, c(mixedsort(names(pred.convergent)))]

strategy.id <- as.numeric(unlist(which(attobo$attribution == "Strategy")))
effort.id <- as.numeric(unlist(which(attobo$attribution == "Effort")))
aptitude.id <- as.numeric(unlist(which(attobo$attribution == "Aptitude")))

pred.convergent$strategy.sim <- apply(pred.convergent[, strategy.id], 1, mean)
pred.convergent$effort.sim <- apply(pred.convergent[, effort.id], 1, mean)
pred.convergent$aptitude.sim <- apply(pred.convergent[, aptitude.id], 1, mean)

quantile(pred.convergent$strategy.sim, probs = c(.025, .5, .975))
quantile(pred.convergent$effort.sim, probs = c(.025, .5, .975))
quantile(pred.convergent$aptitude.sim, probs = c(.025, .5, .975))

```

```{r}

error.convergent <- attobo.out[, grep("error[", colnames(attobo.out), fixed = T)]
#save(error.convergent, file = "error.convergent.RData")

error <- as.vector(unlist(lapply(error.convergent, mean)))
mean(error)
plot(density(error))

```



## Expected Counts for each attribution

```{r echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
attobo.posterior.coefs <- select(pred.convergent, `strategy.sim`, `effort.sim`,`aptitude.sim`)
names(attobo.posterior.coefs) <- c("Strategy", "Effort", "Aptitude")

attobo.posterior.coefs.long <- gather(attobo.posterior.coefs)
#head(attobo.posterior.coefs.long)


```

```{r}
library("ggridges")
ggplot(data = attobo.posterior.coefs.long, aes(x = value, y = key)) + 
  stat_density_ridges(quantile_lines = TRUE, 
                      quantiles = c(0.025, 0.5, 0.975), 
                      alpha = 0.7)
```

```{r}
attobo.posterior.coefs.sum <- summarize(group_by(attobo.posterior.coefs.long, key),
                                        median_coef = median(value),
                                        lower_coef = quantile(value, probs = c(0.025)),
                                        upper_coef = quantile(value, probs = c(0.975)))

convergent.summary <- attobo.posterior.coefs.sum
```

###############################################################################




# Bayesian Model - seekhelp Advice

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}


strategy <- ifelse(attobo$attribution == "Strategy", 1,0)
effort <- ifelse(attobo$attribution == "Effort", 1, 0) 

seekhelp <- attobo$seekhelp

attobo.datjags <- list(strategy = strategy, effort = effort, seekhelp = seekhelp, N = nrow(attobo))
attobo.datjags

```

## Model Specification

```{r}

attobo.model <- function() {
  for(i in 1:N){
    # lambda is mean and variance of the poisson distribution
    seekhelp[i] ~ dpois(lambda[i])
    log(lambda[i]) <- b[1] + b[2] * effort[i] + b[3] * strategy[i]
  }
  
  #priors
  b[1] ~ dnorm(0, 0.0025)
  b[2] ~ dnorm(0, 0.0025)
  b[3] ~ dnorm(0, 0.0025)
  
  for (i in 1:N){
    
    error[i] <- lambda[i] - seekhelp[i]
  
  }
  
  
}

```


```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}

attobo.params <- c("b", "lambda", "error")

attobo.params2 <- c("b")

```

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}

b.inits <- seekhelp.freq$coefficients

attobo.inits1 <-  list( "b" = b.inits)
attobo.inits2 <- list( "b" = rep(0, 3) )
attobo.inits3 <- list( "b" = rep(1, 3) )
attobo.inits4 <- list( "b" = rep(-1, 3) )
attobo.inits5 <- list( "b" = rep(2, 3) )
attobo.inits <- list(attobo.inits1, attobo.inits2,attobo.inits3, attobo.inits4,attobo.inits5)

```

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide', eval = FALSE}

set.seed(1128)
attobo.fit <- jags(data = attobo.datjags, inits = attobo.inits, parameters.to.save = attobo.params, 
                n.chains = 5, n.iter = 100000, n.burnin = 10000, model.file = attobo.model)

attobo.fit.upd <- update(attobo.fit, n.iter =1000)
attobo.fit.upd <- autojags(attobo.fit)

set.seed(1128)
attobo.fit.convergence <- jags(data = attobo.datjags, inits = attobo.inits, parameters.to.save = attobo.params2, 
                n.chains = 5, n.iter = 100000, n.burnin = 10000, model.file = attobo.model)

attobo.fit.upd.convergence <- update(attobo.fit.convergence, n.iter =1000)
attobo.fit.upd.convergence <- autojags(attobo.fit.convergence)

```

```{r eval = FALSE}

attobo.fit.mcmc <- as.mcmc(attobo.fit)
#save(attobo.fit.mcmc, file = "attobo.seekhelp.RData")

attobo.fit.convergence.mcmc <- as.mcmc(attobo.fit.convergence)
summary(attobo.fit.convergence.mcmc)

```

## Convergence Diagnostics

```{r figure = TRUE, fig.width=6, fig.height=6, fig.align='center'}
                                      
MCMCtrace(attobo.fit.convergence.mcmc, ind = TRUE, pdf = FALSE )

autocorr.plot(attobo.fit.convergence.mcmc[1], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[2], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[3], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[4], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[5], ask = FALSE)
```

```{r}

attobo.out <- as.data.frame(as.matrix(attobo.fit.mcmc))

pred.seekhelp <- attobo.out[, grep("lambda[", colnames(attobo.out), fixed = T)]

## saving data
#save(attobo.out, file = "attobo.seekhelp.RData")

## estimated count for each participant
pred.seekhelp <- pred.seekhelp[, c(mixedsort(names(pred.seekhelp)))]

strategy.id <- as.numeric(unlist(which(attobo$attribution == "Strategy")))
effort.id <- as.numeric(unlist(which(attobo$attribution == "Effort")))
aptitude.id <- as.numeric(unlist(which(attobo$attribution == "Aptitude")))

pred.seekhelp$strategy.sim <- apply(pred.seekhelp[, strategy.id], 1, mean)
pred.seekhelp$effort.sim <- apply(pred.seekhelp[, effort.id], 1, mean)
pred.seekhelp$aptitude.sim <- apply(pred.seekhelp[, aptitude.id], 1, mean)

mean(pred.seekhelp$strategy.sim)
quantile(pred.seekhelp$strategy.sim, probs = c(.025, .5, .975))
mean(pred.seekhelp$effort.sim)
quantile(pred.seekhelp$effort.sim, probs = c(.025, .5, .975))
mean(pred.seekhelp$aptitude.sim)
quantile(pred.seekhelp$aptitude.sim, probs = c(.025, .5, .975))


```

```{r}

error.seekhelp <- attobo.out[, grep("error[", colnames(attobo.out), fixed = T)]
#save(error.seekhelp, file = "error.seekhelp.RData")

error <- as.vector(unlist(lapply(error.seekhelp, mean)))

mean(error)

plot(density(error))

```



## Expected Counts for each attribution

```{r echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
attobo.posterior.coefs <- select(pred.seekhelp, `strategy.sim`, `effort.sim`,`aptitude.sim`)
names(attobo.posterior.coefs) <- c("Strategy", "Effort", "Aptitude")

attobo.posterior.coefs.long <- gather(attobo.posterior.coefs)
#head(attobo.posterior.coefs.long)


```

```{r}
library("ggridges")
ggplot(data = attobo.posterior.coefs.long, aes(x = value, y = key)) + 
  stat_density_ridges(quantile_lines = TRUE, 
                      quantiles = c(0.025, 0.5, 0.975), 
                      alpha = 0.7)
```

###############################################################################



# expectancy

## Bayesian Model - expectancy

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}
library(R2jags)
library(rjags)
library(runjags)
library("lattice")
library("superdiag")
library(gtools)

library(bayestestR) 
library("ggmcmc")


strategy <- ifelse(attobo$attribution == "Strategy", 1,0)
effort <- ifelse(attobo$attribution == "Effort", 1, 0) 

attobo.datjags <- list(strategy = strategy, effort = effort, N = nrow(attobo), expectancy = expectancy)
attobo.datjags
```

## Model Specification

```{r}

attobo.model <- function() {
  
  for(i in 1:N){
  
    expectancy[i] ~ dbeta(alpha[i], beta[i])
    alpha[i] = phi * mu[i]
    beta[i] = phi * (1 - mu[i])
    logit(mu[i]) <- b[1] + b[2] * effort[i] + b[3] * strategy[i]
  }
  
  #priors
  
 for(i in 1:3){
   b[i] ~ dnorm(0, 0.0025) 
 }
  
    phiinv ~ dgamma(0.01,0.01)
   phi <- 1/phiinv 

  
  #calculations
  for (i in 1:N){
    
    error[i] <- mu[i] - expectancy[i]
    
  }
  
}

```


```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}

attobo.params <- c("b", "mu", "error")

attobo.params2 <- c("b")

```

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}

b.inits <- expectancy.freq$coefficients$mean

attobo.inits1 <-  list( "b" = b.inits, "phiinv" = 1)
attobo.inits2 <- list( "b" = rep(0, 3) , "phiinv" =2 )
attobo.inits3 <- list( "b" = rep(1, 3), "phiinv" = 1 )
attobo.inits4 <- list( "b" = rep(-1, 3) , "phiinv" = 2 )
attobo.inits5 <- list( "b" = rep(2, 3), "phiinv" = 1 )
attobo.inits <- list(attobo.inits1, attobo.inits2,attobo.inits3, attobo.inits4,attobo.inits5)

```

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide', eval = FALSE}

set.seed(1128)
attobo.fit <- jags(data = attobo.datjags, inits = attobo.inits, parameters.to.save = attobo.params, 
                n.chains = 5, n.iter = 100000, n.burnin = 10000, model.file = attobo.model)

attobo.fit.upd <- update(attobo.fit, n.iter =1000)
attobo.fit.upd <- autojags(attobo.fit)

```

```{r eval = FALSE}

attobo.fit.mcmc <- as.mcmc(attobo.fit)
#save(attobo.fit.mcmc, file = "attobo.expectancy.RData")

```

## Convergence Diagnostics

```{r figure = TRUE, fig.width=6, fig.height=6, fig.align='center'}

MCMCtrace(attobo.fit.mcmc[, 1:4] , ind = TRUE, pdf = FALSE )

autocorr.plot(attobo.fit.mcmc[1][, 1:4], ask = FALSE)

autocorr.plot(attobo.fit.mcmc[2][, 1:4], ask = FALSE)

autocorr.plot(attobo.fit.mcmc[3][, 1:4], ask = FALSE)

autocorr.plot(attobo.fit.mcmc[4][, 1:4], ask = FALSE)

autocorr.plot(attobo.fit.mcmc[5][, 1:4], ask = FALSE)
```

```{r}

attobo.out <- as.data.frame(as.matrix(attobo.fit.mcmc))

pred.expectancy <- attobo.out[, grep("mu[", colnames(attobo.out), fixed = T)]

## saving data
#save(attobo.out, file = "attobo.expectancy.RData")

## estimated count for each participant
pred.expectancy <- pred.expectancy[, c(mixedsort(names(pred.expectancy)))]

strategy.id <- as.numeric(unlist(which(attobo$attribution == "Strategy")))
effort.id <- as.numeric(unlist(which(attobo$attribution == "Effort")))
aptitude.id <- as.numeric(unlist(which(attobo$attribution == "Aptitude")))

pred.expectancy$strategy.sim <- apply(pred.expectancy[, strategy.id], 1, mean)
pred.expectancy$effort.sim <- apply(pred.expectancy[, effort.id], 1, mean)
pred.expectancy$aptitude.sim <- apply(pred.expectancy[, aptitude.id], 1, mean)

quantile(pred.expectancy$strategy.sim, probs = c(.025, .5, .975))
quantile(pred.expectancy$effort.sim, probs = c(.025, .5, .975))
quantile(pred.expectancy$aptitude.sim, probs = c(.025, .5, .975))

mean(pred.expectancy$effort.sim)
mean(pred.expectancy$strategy.sim)
mean(pred.expectancy$aptitude.sim)
```

```{r}

error.expectancy <- attobo.out[, grep("error[", colnames(attobo.out), fixed = T)]
#save(error.expectancy, file = "error.expectancy.RData")


error <- as.vector(unlist(lapply(error.expectancy, mean)))
mean(error)
plot(density(error))

```



## Expected Counts for each attribution

```{r echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
attobo.posterior.coefs <- select(pred.expectancy, `strategy.sim`, `effort.sim`,`aptitude.sim`)
names(attobo.posterior.coefs) <- c("Strategy", "Effort", "Aptitude")

attobo.posterior.coefs.long <- gather(attobo.posterior.coefs)
#head(attobo.posterior.coefs.long)


```

```{r}
library("ggridges")
ggplot(data = attobo.posterior.coefs.long, aes(x = value, y = key)) + 
  stat_density_ridges(quantile_lines = TRUE, 
                      quantiles = c(0.025, 0.5, 0.975), 
                      alpha = 0.7)
```




# Bayesian Model - total Advice

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}

strategy <- ifelse(attobo$attribution == "Strategy", 1,0)
effort <- ifelse(attobo$attribution == "Effort", 1, 0) 

total <- attobo$total

attobo.datjags <- list(strategy = strategy, effort = effort, total = total, N = nrow(attobo))
attobo.datjags

```

## Model Specification

```{r}

attobo.model <- function() {
  for(i in 1:N){
    # lambda is mean and variance of the poisson distribution
    total[i] ~ dpois(lambda[i])
    log(lambda[i]) <- b[1] + b[2] * effort[i] + b[3] * strategy[i]
  }
  
  #priors
  b[1] ~ dnorm(0, 0.0025)
  b[2] ~ dnorm(0, 0.0025)
  b[3] ~ dnorm(0, 0.0025)
  
  for (i in 1:N){
    
    error[i] <- lambda[i] - total[i]
  
  }
  
  
}

```


```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}

attobo.params <- c("b", "lambda", "error")

attobo.params2 <- c("b")

```

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}

b.inits <- total.freq$coefficients

attobo.inits1 <-  list( "b" = b.inits)
attobo.inits2 <- list( "b" = rep(0, 3) )
attobo.inits3 <- list( "b" = rep(1, 3) )
attobo.inits4 <- list( "b" = rep(-1, 3) )
attobo.inits5 <- list( "b" = rep(2, 3) )
attobo.inits <- list(attobo.inits1, attobo.inits2,attobo.inits3, attobo.inits4,attobo.inits5)

```

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide', eval = FALSE}

set.seed(1128)
attobo.fit <- jags(data = attobo.datjags, inits = attobo.inits, parameters.to.save = attobo.params, 
                n.chains = 5, n.iter = 100000, n.burnin = 10000, model.file = attobo.model)

attobo.fit.upd <- update(attobo.fit, n.iter =1000)
attobo.fit.upd <- autojags(attobo.fit)

set.seed(1128)
attobo.fit.convergence <- jags(data = attobo.datjags, inits = attobo.inits, parameters.to.save = attobo.params2, 
                n.chains = 5, n.iter = 100000, n.burnin = 10000, model.file = attobo.model)

attobo.fit.upd.convergence <- update(attobo.fit.convergence, n.iter =1000)
attobo.fit.upd.convergence <- autojags(attobo.fit.convergence)

```

```{r eval = FALSE}

attobo.fit.mcmc <- as.mcmc(attobo.fit)
#save(attobo.fit.mcmc, file = "attobo.total.RData")

attobo.fit.convergence.mcmc <- as.mcmc(attobo.fit.convergence)
summary(attobo.fit.convergence.mcmc)

```

## Convergence Diagnostics

```{r figure = TRUE, fig.width=6, fig.height=6, fig.align='center'}
                                      
MCMCtrace(attobo.fit.convergence.mcmc, ind = TRUE, pdf = FALSE )

autocorr.plot(attobo.fit.convergence.mcmc[1], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[2], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[3], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[4], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[5], ask = FALSE)
```

```{r}

attobo.out <- as.data.frame(as.matrix(attobo.fit.mcmc))

pred.total <- attobo.out[, grep("lambda[", colnames(attobo.out), fixed = T)]

## saving data
#save(attobo.out, file = "attobo.total.RData")

## estimated count for each participant
pred.total <- pred.total[, c(mixedsort(names(pred.total)))]

strategy.id <- as.numeric(unlist(which(attobo$attribution == "Strategy")))
effort.id <- as.numeric(unlist(which(attobo$attribution == "Effort")))
aptitude.id <- as.numeric(unlist(which(attobo$attribution == "Aptitude")))

pred.total$strategy.sim <- apply(pred.total[, strategy.id], 1, mean)
pred.total$effort.sim <- apply(pred.total[, effort.id], 1, mean)
pred.total$aptitude.sim <- apply(pred.total[, aptitude.id], 1, mean)

quantile(pred.total$strategy.sim, probs = c(.025, .5, .975))
quantile(pred.total$effort.sim, probs = c(.025, .5, .975))
quantile(pred.total$aptitude.sim, probs = c(.025, .5, .975))

pred.total$diff.1 <- pred.total$strategy.sim - pred.total$aptitude.sim
pred.total$diff.2 <- pred.total$strategy.sim - pred.total$effort.sim
pred.total$diff.3 <- pred.total$effort.sim - pred.total$aptitude.sim

quantile(pred.total$diff.1, probs = c(.025, .5, .975))
quantile(pred.total$diff.2, probs = c(.025, .5, .975))
quantile(pred.total$diff.3, probs = c(.025, .5, .975))

```

```{r}

error.total <- attobo.out[, grep("error[", colnames(attobo.out), fixed = T)]
#save(error.total, file = "error.total.RData")

error <- as.vector(unlist(lapply(error.total, mean)))
mean(error)
plot(density(error))

```



## Expected Counts for each attribution

```{r echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
attobo.posterior.coefs <- select(pred.total, `strategy.sim`, `effort.sim`,`aptitude.sim`)
names(attobo.posterior.coefs) <- c("Strategy", "Effort", "Aptitude")

attobo.posterior.coefs.long <- gather(attobo.posterior.coefs)
#head(attobo.posterior.coefs.long)


```

```{r}
library("ggridges")
ggplot(data = attobo.posterior.coefs.long, aes(x = value, y = key)) + 
  stat_density_ridges(quantile_lines = TRUE, 
                      quantiles = c(0.025, 0.5, 0.975), 
                      alpha = 0.7)
```

###############################################################################


# Bayesian Model - combined method Advice

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}

strategy <- ifelse(attobo$attribution == "Strategy", 1,0)
effort <- ifelse(attobo$attribution == "Effort", 1, 0) 

combined <- attobo$combined_method

attobo.datjags <- list(strategy = strategy, effort = effort, combined = combined, N = nrow(attobo))
attobo.datjags

```

## Model Specification

```{r}

attobo.model <- function() {
  for(i in 1:N){
    # lambda is mean and variance of the poisson distribution
    combined[i] ~ dpois(lambda[i])
    log(lambda[i]) <- b[1] + b[2] * effort[i] + b[3] * strategy[i]
  }
  
  #priors
  b[1] ~ dnorm(0, 0.0025)
  b[2] ~ dnorm(0, 0.0025)
  b[3] ~ dnorm(0, 0.0025)
  
  for (i in 1:N){
    
    error[i] <- lambda[i] - combined[i]
  
  }
  
  
}

```


```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}

attobo.params <- c("b", "lambda", "error")

attobo.params2 <- c("b")

```

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide'}

b.inits <- combined.freq$coefficients

attobo.inits1 <-  list( "b" = b.inits)
attobo.inits2 <- list( "b" = rep(0, 3) )
attobo.inits3 <- list( "b" = rep(1, 3) )
attobo.inits4 <- list( "b" = rep(-1, 3) )
attobo.inits5 <- list( "b" = rep(2, 3) )
attobo.inits <- list(attobo.inits1, attobo.inits2,attobo.inits3, attobo.inits4,attobo.inits5)

```

```{r echo=FALSE, warning = FALSE, message = FALSE, results='hide', eval = FALSE}

set.seed(1128)
attobo.fit <- jags(data = attobo.datjags, inits = attobo.inits, parameters.to.save = attobo.params, 
                n.chains = 5, n.iter = 100000, n.burnin = 10000, model.file = attobo.model)

attobo.fit.upd <- update(attobo.fit, n.iter =1000)
attobo.fit.upd <- autojags(attobo.fit)

set.seed(1128)
attobo.fit.convergence <- jags(data = attobo.datjags, inits = attobo.inits, parameters.to.save = attobo.params2, 
                n.chains = 5, n.iter = 100000, n.burnin = 10000, model.file = attobo.model)

attobo.fit.upd.convergence <- update(attobo.fit.convergence, n.iter =1000)
attobo.fit.upd.convergence <- autojags(attobo.fit.convergence)

```

```{r eval = FALSE}

attobo.fit.mcmc <- as.mcmc(attobo.fit)
#save(attobo.fit.mcmc, file = "attobo.combined.RData")

attobo.fit.convergence.mcmc <- as.mcmc(attobo.fit.convergence)
summary(attobo.fit.convergence.mcmc)

```

## Convergence Diagnostics

```{r figure = TRUE, fig.width=6, fig.height=6, fig.align='center'}
                                      
MCMCtrace(attobo.fit.convergence.mcmc, ind = TRUE, pdf = FALSE )

autocorr.plot(attobo.fit.convergence.mcmc[1], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[2], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[3], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[4], ask = FALSE)

autocorr.plot(attobo.fit.convergence.mcmc[5], ask = FALSE)
```

```{r}

attobo.out <- as.data.frame(as.matrix(attobo.fit.mcmc))

pred.combined <- attobo.out[, grep("lambda[", colnames(attobo.out), fixed = T)]

## saving data
#save(attobo.out, file = "attobo.combined.RData")

## estimated count for each participant
pred.combined <- pred.combined[, c(mixedsort(names(pred.combined)))]

strategy.id <- as.numeric(unlist(which(attobo$attribution == "Strategy")))
effort.id <- as.numeric(unlist(which(attobo$attribution == "Effort")))
aptitude.id <- as.numeric(unlist(which(attobo$attribution == "Aptitude")))

pred.combined$strategy.sim <- apply(pred.combined[, strategy.id], 1, mean)
pred.combined$effort.sim <- apply(pred.combined[, effort.id], 1, mean)
pred.combined$aptitude.sim <- apply(pred.combined[, aptitude.id], 1, mean)

quantile(pred.combined$strategy.sim, probs = c(.025, .5, .975))
quantile(pred.combined$effort.sim, probs = c(.025, .5, .975))
quantile(pred.combined$aptitude.sim, probs = c(.025, .5, .975))

```

```{r}

error.combined <- attobo.out[, grep("error[", colnames(attobo.out), fixed = T)]
#save(error.combined, file = "error.combined.RData")

error <- as.vector(unlist(lapply(error.combined, mean)))
mean(error)
plot(density(error))

```



## Expected Counts for each attribution

```{r echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
attobo.posterior.coefs <- select(pred.combined, `strategy.sim`, `effort.sim`,`aptitude.sim`)
names(attobo.posterior.coefs) <- c("Strategy", "Effort", "Aptitude")

attobo.posterior.coefs.long <- gather(attobo.posterior.coefs)
#head(attobo.posterior.coefs.long)


```

```{r}
library("ggridges")
ggplot(data = attobo.posterior.coefs.long, aes(x = value, y = key)) + 
  stat_density_ridges(quantile_lines = TRUE, 
                      quantiles = c(0.025, 0.5, 0.975), 
                      alpha = 0.7)
```

```{r}
attobo.posterior.coefs.sum <- summarize(group_by(attobo.posterior.coefs.long, key),
                                        median_coef = median(value),
                                        lower_coef = quantile(value, probs = c(0.025)),
                                        upper_coef = quantile(value, probs = c(0.975)))

combined.summary <- attobo.posterior.coefs.sum
```

