---
title: "Study 1 Analysis (Workplace Domain)"
author: "Dennis W.H. Teo"
output: 
  html_document:
    theme: darkly
    toc: yes
    toc_depth: 3
    toc_float: true
    highlight: tango
    df_print: paged
    fig_caption: false
    code_fold: hide
fontsize: 18pt
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message=FALSE)
```

```{r results='hide', eval=TRUE, warning=F, message=F}

library(psych)
library(ggplot2)
library(effects)
## Library for the multiple comparisons
library(phia)
## Library to compute the effect sizes
library(sjstats)
library(lsr)
library(lavaan)
library(ggthemes)
library(tibble)
library(car)
library(olsrr)
library(pwr)
library(car)
library(tidyverse)
library(glm2)
library(betareg)
library(multcomp)
library(dthelper)

select <- dplyr::select

reverse.logodds <- function(x){
  exp(x)/(1+exp(x))
}

report <- function(x,dp=2){
  m <- round(mean(x, na.rm=T),dp)
  s <- round(sd(x, na.rm=T),dp)
  return(paste0(m, " (", s, ")"))
}

```

```{r eval=TRUE}

library(readr)
attobo <- read_csv("attobo1_clean.csv")

```

```{r  results='hide', eval=TRUE}

# failure$scenario <- as.factor(failure$scenario)
attobo$scenario <- as.factor(attobo$scenario)
# success$scenario <- as.factor(success$scenario)
attobo$valence <- as.factor(attobo$valence)
attobo$attribution <- as.factor(attobo$attribution)

attobo$expectancy <- (attobo$expectancy - 1)/10
attobo$expectancy <- ifelse(attobo$expectancy == 1, .999,
                     ifelse(attobo$expectancy == 0, .001, attobo$expectancy) )

attobo$attribution_effort <- factor(attobo$attribution, levels = c("Effort", "Strategy", "Aptitude"))
attobo$attribution_strat <- factor(attobo$attribution, levels = c( "Strategy","Effort", "Aptitude"))

attobo$redo.feedback <- ifelse(attobo$redo == 1 & attobo$method == 1, 1,0)

attobo$redo.nofeedback <- ifelse(attobo$redo == 1 & attobo$method == 0, 1,0)

attobo <- attobo %>% 
  filter(valence == "Fail") %>%
  rename(workharder = bruteforce)

```




# Descriptive Stats

## Sample Breakdown

```{r}
## Sample Breakdown
attobo %>%
  mutate(`Attibution Condition` = attribution) %>%
  group_by(`Attibution Condition`) %>%
  summarise(N = n())
```

## Histograms of Collected Measures

```{r eval=TRUE}

attobo.advice <- attobo %>%
  select(method, workharder, threat, tangiblerewards,
         switch, expectancy)

attobo.attribution <- attobo %>%
  select(aptout, aptvar, aptuncon, 
         effortout, effortvar, effortuncon,
         stratout, stratvar, stratuncon,
         luckout, luckvar, luckuncon,
         taskout, taskvar, taskuncon,
         moodout, moodvar, mooduncon)

attobo.others <- attobo %>%
  select(gender, age, education, sms,
         smo, so, race)

ggplot(data = gather(attobo.advice, factor_key = TRUE), aes(x = factor(value))) +
  geom_bar() + 
  facet_wrap(~ key,scales = "free", as.table = TRUE, nrow = 3) + xlab("") + 
  theme_bw()

ggplot(data = gather(attobo.attribution, factor_key = TRUE), aes(x = factor(value))) +
  geom_bar() + 
  facet_wrap(~ key,scales = "free", as.table = TRUE, nrow = 3) + xlab("") + 
  theme_bw()

ggplot(data = gather(attobo.others, factor_key = TRUE), aes(x = factor(value))) +
  geom_bar() + 
  facet_wrap(~ key,scales = "free", as.table = TRUE, nrow = 3) + xlab("") + 
  theme_bw()

```


# Main Analysis

## Work Harder Advice {.tabset}

### Model and Hypothesis test


```{r}

workharder.model <- glm2(workharder ~ attribution_effort, data = attobo, family = binomial(link = "logit"))


summary(workharder.model)
confint(workharder.model)
Anova(workharder.model)

# compute effect size
model.anova <- car::Anova(workharder.model)
cohen.w <- sqrt(model.anova$`LR Chisq`[1]/(1*nrow(attobo)))
print(paste("Cohen W:", round(cohen.w,3) ))

```

### Converted Estimates (to probability)

```{r}

workharder.coefs <- summary(workharder.model)$coefficients

workharder.summary <- data.frame(
  advice = rep("Work Harder",3),
  attribution = c("Effort","Strategy","Aptitude"),
  mean = c(reverse.logodds(workharder.coefs[1, "Estimate"]), reverse.logodds(workharder.coefs[1, "Estimate"] + workharder.coefs[2, "Estimate"]), reverse.logodds(workharder.coefs[1, "Estimate"] + workharder.coefs[3, "Estimate"])),
  lower = c(reverse.logodds(confint(workharder.model)[1,])[1], reverse.logodds(workharder.coefs[1, "Estimate"] + confint(workharder.model)[2,])[1], reverse.logodds(workharder.coefs[1, "Estimate"] + confint(workharder.model)[3,])[1]),
  upper = c(reverse.logodds(confint(workharder.model)[1,])[2], reverse.logodds(workharder.coefs[1, "Estimate"] + confint(workharder.model)[2,])[2], reverse.logodds(workharder.coefs[1, "Estimate"] + confint(workharder.model)[3,])[2])
)

coef.summary <- workharder.summary

colnames(workharder.summary) <- c("Advice", "Attribution", "Mean", "Lower", "Upper")
workharder.summary

```

## Methodological Advice {.tabset}

### Model and Hypothesis test


```{r}
method.model <- glm2(method ~ attribution_strat, data = attobo, family = binomial(link = "logit"))

summary(method.model)
confint(method.model)
Anova(method.model)

# compute effect size
model.anova <- car::Anova(method.model)
cohen.w <- sqrt(model.anova$`LR Chisq`[1]/(1*nrow(attobo)))
print(paste("Cohen W:", round(cohen.w,3) ))

```

### Converted Estimates (to probability)

```{r }

method.coefs <- summary(method.model)$coefficients

method.summary <- data.frame(
  advice = rep("Methodological",3),
  attribution = c("Strategy", "Effort","Aptitude"),
  mean = c(reverse.logodds(method.coefs[1, "Estimate"]), reverse.logodds(method.coefs[1, "Estimate"] + method.coefs[2, "Estimate"]), reverse.logodds(method.coefs[1, "Estimate"] + method.coefs[3, "Estimate"])),
  lower = c(reverse.logodds(confint(method.model)[1,])[1], reverse.logodds(method.coefs[1, "Estimate"] + confint(method.model)[2,])[1], reverse.logodds(method.coefs[1, "Estimate"] + confint(method.model)[3,])[1]),
  upper = c(reverse.logodds(confint(method.model)[1,])[2], reverse.logodds(method.coefs[1, "Estimate"] + confint(method.model)[2,])[2], reverse.logodds(method.coefs[1, "Estimate"] + confint(method.model)[3,])[2])
)

coef.summary <- rbind(coef.summary, method.summary)

colnames(workharder.summary) <- c("Advice", "Attribution", "Mean", "Lower", "Upper")
workharder.summary

```


## Try Again Advice {.tabset}

### Model and Hypothesis test


```{r}
redo.model <- glm2(redo ~ attribution_effort, data = attobo, family = binomial(link = "logit"))

summary(redo.model)
confint(redo.model)
Anova(redo.model)

# compute effect size
model.anova <- car::Anova(redo.model)
cohen.w <- sqrt(model.anova$`LR Chisq`[1]/(1*nrow(attobo)))
print(paste("Cohen W:", round(cohen.w,3) ))

```

### Converted Estimates (to probability)

```{r}

redo.coefs <- summary(redo.model)$coefficients

redo.summary <- data.frame(
  advice = rep("Try Again",3),
  attribution = c("Effort","Strategy","Aptitude"),
  mean = c(reverse.logodds(redo.coefs[1, "Estimate"]), reverse.logodds(redo.coefs[1, "Estimate"] + redo.coefs[2, "Estimate"]), reverse.logodds(redo.coefs[1, "Estimate"] + redo.coefs[3, "Estimate"])),
  lower = c(reverse.logodds(confint(redo.model)[1,])[1], reverse.logodds(redo.coefs[1, "Estimate"] + confint(redo.model)[2,])[1], reverse.logodds(redo.coefs[1, "Estimate"] + confint(redo.model)[3,])[1]),
  upper = c(reverse.logodds(confint(redo.model)[1,])[2], reverse.logodds(redo.coefs[1, "Estimate"] + confint(redo.model)[2,])[2], reverse.logodds(redo.coefs[1, "Estimate"] + confint(redo.model)[3,])[2])
)

coef.summary <- rbind(coef.summary, redo.summary)

colnames(redo.summary) <- c("Advice", "Attribution", "Mean", "Lower", "Upper")
redo.summary
```

## Expectancy {.tabset}

### Model and Hypothesis test


```{r}
expectancy.model <- betareg(expectancy ~ attribution, data = attobo, link = "logit" )

summary(expectancy.model)
confint(expectancy.model)
Anova(expectancy.model)


```

### Converted Estimates (to probability)

```{r}
expectancy.coefs <- summary(expectancy.model)$coefficients$mean

expectancy.summary <- data.frame(
  attribution = c("Effort", "Strategy","Aptitude"),
  mean = c(reverse.logodds(expectancy.coefs[1, "Estimate"] + expectancy.coefs[2, "Estimate"]), reverse.logodds(expectancy.coefs[1, "Estimate"] + expectancy.coefs[3, "Estimate"]), reverse.logodds(expectancy.coefs[1, "Estimate"])),
  lower = c(reverse.logodds(expectancy.coefs[1, "Estimate"] + confint(expectancy.model)[2,])[1], reverse.logodds(expectancy.coefs[1, "Estimate"] + confint(expectancy.model)[3,])[1], reverse.logodds(confint(expectancy.model)[1,])[1]),
  upper = c(reverse.logodds(expectancy.coefs[1, "Estimate"] + confint(expectancy.model)[2,])[2], reverse.logodds(expectancy.coefs[1, "Estimate"] + confint(expectancy.model)[3,])[2], reverse.logodds(confint(expectancy.model)[1,])[2])
)
colnames(expectancy.summary) <- c("Attribution", "Mean", "Lower", "Upper")
expectancy.summary
```


# Graphs

```{r}
colnames(coef.summary) <- c("Advice", "Attribution", "Mean", "Lower", "Upper")

coef.summary$Advice <- factor(coef.summary$Advice, levels = c("Work Harder", "Methodological","Try Again"))

coef.summary$Attribution <- factor(coef.summary$Attribution, levels = c("Effort", "Strategy", "Aptitude"))

coef.summary
```


```{r}

attobo.advice.full.plot <-  ggplot(coef.summary, aes(x = Attribution, y = Mean, shape = Advice)) + 
  geom_errorbar( aes(ymin=Lower, ymax=Upper), width=.2,
                 position=position_dodge(.4)) +
  geom_point(aes(col = Advice), position=position_dodge(.4), size = 4) +
  scale_color_manual(values = c("#D55E00", "#0072B2", "#E69F00")) +
  scale_shape_manual(values = c(16,17,18))+
  ylab("Probability of Advice") + xlab("") + 
  theme_bw() +
  theme(text = element_text(size = 16),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())


attobo.advice.full.plot

```




