---
title: "Pre-test Analysis"
author: "Dennis Teo"
output:
  html_document:
    theme: readable
    toc: yes
    toc_depth: 3
    toc_float: true
    highlight: tango
    df_print: paged
fontsize: 18pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

```{r echo=FALSE, results='hide'}

library(psych)
library(ggplot2)
library(tidyverse)
library(effects)
## Library for the multiple comparisons
library(phia)
## Library to compute the effect sizes
library(sjstats)
library(lsr)
library(lavaan)
library(ggthemes)
library(tibble)
library(car)
library(olsrr)

library(R2jags)
library(rjags)
library(runjags)
library("lattice")
library("superdiag")
library(gtools)

library(bayestestR) 
library("ggmcmc")
library(brms)
library(BayesFactor)
library(MCMCvis)

load("attobo.pilot.RData")

source('Useful Code V2.R')

```

```{r}


attobo.pilot$Age[attobo.pilot$Age == 1943] <- 75
attobo.pilot$Age[attobo.pilot$Age == 1984] <- 34
attobo.pilot$Age[attobo.pilot$Age == 1987] <- 31
attobo.pilot$Age[attobo.pilot$Age == 1988] <- 32
attobo.pilot$Age[attobo.pilot$Age == 1992] <- 26

summary(attobo.pilot$Age)

sd(attobo.pilot$Age, na.rm = T)

summary(factor(attobo.pilot$Gender))


```


```{r}

attobo.pilot$row.id <- 1:202

attobo.locus.long <- data.frame(
  
  locus = c(attobo.pilot$AptOut, attobo.pilot$EffortOut, attobo.pilot$StratOut),
  id = rep(attobo.pilot$row.id, 3),
  attribution = c(rep("Aptitude", 202), rep("Effort", 202), rep("Strategy", 202))
  # effort = c(rep(0, 202), rep(1,202), rep(0, 202)), 
  # strategy = c(rep(0, 202), rep(0,202), rep(1, 202)), 
  # effort = c(rep(1, 202), rep(0,202), rep(0, 202))
  
)

attobo.var.long <- data.frame(
  
  var = c(attobo.pilot$AptVar, attobo.pilot$EffortVar, attobo.pilot$StratVar),
  id = rep(attobo.pilot$row.id, 3),
  attribution = c(rep("Aptitude", 202), rep("Effort", 202), rep("Strategy", 202))
  
)

attobo.uncon.long <- data.frame(
  
  uncon = c(attobo.pilot$AptUncon, attobo.pilot$EffortUncon, attobo.pilot$StratUncon),
  id = rep(attobo.pilot$row.id, 3),
  attribution = c(rep("Aptitude", 202), rep("Effort", 202), rep("Strategy", 202))
  
)

```


# Descriptive Stats

```{r }

attobo.pilot %>%
  summarise(AptOutMean = mean(AptOut, na.rm = T),
            EffortOutMean = mean(EffortOut, na.rm = T),
            StratOutMean = mean(StratOut, na.rm = T),
            AptOutSD = sd(AptOut, na.rm = T),
            EffortOutSD = sd(EffortOut, na.rm = T),
            StratOutSD = sd(StratOut, na.rm = T))

attobo.pilot %>%
  summarise(AptVarMean = mean(AptVar, na.rm = T),
            EffortVarMean = mean(EffortVar, na.rm = T),
            StratVarMean = mean(StratVar, na.rm = T),
            AptVarSD = sd(AptVar, na.rm = T),
            EffortVarSD = sd(EffortVar, na.rm = T),
            StratVarSD = sd(StratVar, na.rm = T))

attobo.pilot %>%
  summarise(AptUnconMean = mean(AptUncon, na.rm = T),
            EffortUnconMean = mean(EffortUncon, na.rm = T),
            StratUnconMean = mean(StratUncon, na.rm = T),
            AptUnconSD = sd(AptUncon, na.rm = T),
            EffortUnconSD = sd(EffortUncon, na.rm = T),
            StratUnconSD = sd(StratUncon, na.rm = T))

attobo.dimensions <- attobo.pilot[, 2:19]

ggplot(data = gather(attobo.dimensions , factor_key = TRUE), aes(x = factor(value))) +
  geom_bar() + 
  facet_wrap(~ key,scales = "free", as.table = TRUE, nrow = 3) + xlab("") + 
  theme_bw()


```

###################################################################

# Attribution Patterns

## Locus

### Frequentist Estimates

```{r}

t.test(attobo.pilot$EffortOut, attobo.pilot$AptOut, paired = TRUE)

t.test(attobo.pilot$StratOut, attobo.pilot$AptOut,paired = TRUE)

t.test(attobo.pilot$StratOut, attobo.pilot$EffortOut, paired = TRUE)


```

### Bayesian Model - Locus


```{r eval = F}

apt.out <- attobo.pilot$AptOut
eff.out <- attobo.pilot$EffortOut
strat.out <- attobo.pilot$StratOut

y <- c(apt.out, eff.out, strat.out)
grand.mean <- mean(y, na.rm = T)

attobo.pilot.datjags <- list(apt.out = apt.out, eff.out = eff.out, strat.out = strat.out, N = nrow(attobo.pilot), grand.mean = grand.mean)
attobo.pilot.datjags
```


### Model Specification

```{r eval = F}

attobo.pilot.model <- function() {
  for(i in 1:N){
    # lambda is mean and variance of the poisson distribution
    
    apt.out[i] ~ dnorm(mu.apt[i], sigma[i]) # fixing error from each participant to be the same
    eff.out[i] ~ dnorm(mu.eff[i], sigma[i])
    strat.out[i] ~ dnorm(mu.strat[i], sigma[i])
    sigma[i] ~ dgamma(.01, .01) # all errors come from same distribution
  
    diff[1, i] <- mu.eff[i] - mu.apt[i]
    diff[2, i] <- mu.strat[i] - mu.apt[i]
    diff[3, i] <- mu.strat[i] - mu.eff[i]

    #priors
    mu.apt[i] ~ dnorm(grand.mean, .01)
    mu.eff[i] ~ dnorm(grand.mean, .01)
    mu.strat[i] ~ dnorm(grand.mean, .01)
    
  }
   
  
}
  
  

```


```{r eval = F}

attobo.pilot.params <- c("diff", "mu.apt", "mu.eff", "mu.strat", "sigma")

```

```{r eval = F}



attobo.pilot.inits1 <-  list( "mu.apt" =  rep(grand.mean, 202),
                        "mu.eff" = rep(grand.mean, 202), 
                        "mu.strat" = rep(grand.mean, 202),
                        "sigma" = rep(1,202))
attobo.pilot.inits2 <- list( "mu.apt" =  rep(3.5, 202),
                        "mu.eff" = rep(3.5, 202), 
                        "mu.strat" = rep(3.5, 202),
                        "sigma" = rep(2,202))
attobo.pilot.inits3 <- list( "mu.apt" =  rep(5, 202),
                        "mu.eff" = rep(5, 202), 
                        "mu.strat" = rep(5, 202),
                        "sigma" = rep(3,202))
attobo.pilot.inits4 <- list( "mu.apt" =  rep(2.5, 202),
                        "mu.eff" = rep(2.5, 202), 
                        "mu.strat" = rep(2.5, 202),
                        "sigma" = rep(1,202))
attobo.pilot.inits5 <- list( "mu.apt" =  rep(6, 202),
                        "mu.eff" = rep(6, 202), 
                        "mu.strat" = rep(6, 202),
                        "sigma" = rep(5,202))

attobo.pilot.inits <- list(attobo.pilot.inits1, attobo.pilot.inits2,attobo.pilot.inits3, attobo.pilot.inits4,attobo.pilot.inits5)

```



```{r eval = F}

set.seed(1128)
attobo.pilot.fit <- jags(data = attobo.pilot.datjags, inits = attobo.pilot.inits, parameters.to.save = attobo.pilot.params, 
                n.chains = 5, n.iter = 100000, n.burnin = 10000, model.file = attobo.pilot.model)

attobo.pilot.fit.upd <- update(attobo.pilot.fit, n.iter =1000)
attobo.pilot.fit.upd <- autojags(attobo.pilot.fit)

```

```{r eval = FALSE}

attobo.pilot.fit.mcmc <- as.mcmc(attobo.pilot.fit)
save(attobo.pilot.fit.mcmc, file = "attobo.pilot.locus.mcmc.RData")
summary(attobo.pilot.fit.mcmc)

```

### Convergence Diagnostics

```{r figure = TRUE, fig.width=6, fig.height=6, fig.align='center'}
                                      
load("attobo.pilot.locus.mcmc.RData")

#  15 traces
MCMCtrace(attobo.pilot.fit.mcmc[,1:15], ind = TRUE, pdf = FALSE )

autocorr.plot(attobo.pilot.fit.mcmc[1][,1:15], ask = FALSE)

autocorr.plot(attobo.pilot.fit.mcmc[2][,1:15], ask = FALSE)

autocorr.plot(attobo.pilot.fit.mcmc[3][,1:15], ask = FALSE)

autocorr.plot(attobo.pilot.fit.mcmc[4][,1:15], ask = FALSE)

autocorr.plot(attobo.pilot.fit.mcmc[5][,1:15], ask = FALSE)

```

### Calculating quantiles
```{r eval=F}
attobo.pilot.out <- as.data.frame(as.matrix(attobo.pilot.fit.mcmc))
save(attobo.pilot.out, file = "attobo.pilot.locus.RData")
```


```{r}

load("attobo.pilot.locus.RData")

pred.diff <- attobo.pilot.out[, grep("diff[", colnames(attobo.pilot.out), fixed = T)]

## estimated difference for each participant
pred.diff <- pred.diff[, c(mixedsort(names(pred.diff)))]

diff.1 <- pred.diff[, 1:202]
diff.1$mean.1 <- apply(diff.1, 1, mean)

diff.2 <- pred.diff[, 203:404]
diff.2$mean.2 <- apply(diff.2, 1, mean)

diff.3 <- pred.diff[, 405:606]
diff.3$mean.3 <- apply(diff.3, 1, mean)

# no clear diff
quantile(diff.1$mean.1, probs = c(.025, .5, .975))
# no clear diff
quantile(diff.2$mean.2, probs = c(.025, .5, .975))
# no clear diff
quantile(diff.3$mean.3, probs = c(.025, .5, .975))

```


### Presenting Results

```{r }
attobo.pilot.posterior.coefs <- cbind(diff.1$mean.1, diff.2$mean.2, diff.3$mean.3)
attobo.pilot.posterior.coefs <- as.data.frame(attobo.pilot.posterior.coefs)
names(attobo.pilot.posterior.coefs) <- c("Effort - Aptitude", "Strategy - Aptitude", "Strategy - Effort")

attobo.pilot.posterior.coefs.long <- gather(attobo.pilot.posterior.coefs)


```

```{r}

attobo.pilot.posterior.coefs.sum <- summarize(group_by(attobo.pilot.posterior.coefs.long, key),
                                        median_coef = median(value),
                                        lower_coef = quantile(value, probs = c(0.025)),
                                        upper_coef = quantile(value, probs = c(0.975)))
ggplot(data = attobo.pilot.posterior.coefs.sum, aes(x = median_coef, y = key)) + 
  geom_errorbarh(aes(xmin = lower_coef, xmax = upper_coef), height = 0.1) + 
  geom_point() + 
  geom_vline(xintercept = 0, linetype = "dashed") + 
  xlab("Posterior estimate") + ylab("") + 
  theme_bw()

```


## Variability

### Frequentist Estimates

```{r}

t.test(attobo.pilot$EffortVar, attobo.pilot$AptVar, paired = TRUE)

t.test(attobo.pilot$StratVar, attobo.pilot$AptVar,paired = TRUE)

t.test(attobo.pilot$StratVar, attobo.pilot$EffortVar, paired = TRUE)


```

### Bayesian Model - Variability

```{r eval = F}

apt.var <- attobo.pilot$AptVar
eff.var <- attobo.pilot$EffortVar
strat.var <- attobo.pilot$StratVar

y <- c(apt.var, eff.var, strat.var)
grand.mean <- mean(y, na.rm = T)

attobo.pilot.datjags <- list(apt.var = apt.var, eff.var = eff.var, strat.var = strat.var, N = nrow(attobo.pilot), grand.mean = grand.mean)
attobo.pilot.datjags
```

### Model Specification

```{r eval = F}

attobo.pilot.model <- function() {
  for(i in 1:N){
    # lambda is mean and variance of the poisson distribution
    
    apt.var[i] ~ dnorm(mu.apt[i], sigma[i]) # fixing error from each participant to be the same
    eff.var[i] ~ dnorm(mu.eff[i], sigma[i])
    strat.var[i] ~ dnorm(mu.strat[i], sigma[i])
    sigma[i] ~ dgamma(.01, .01) # all errors come from same distribution
  
    diff[1, i] <- mu.eff[i] - mu.apt[i]
    diff[2, i] <- mu.strat[i] - mu.apt[i]
    diff[3, i] <- mu.strat[i] - mu.eff[i]

    #priors
    mu.apt[i] ~ dnorm(grand.mean, .01)
    mu.eff[i] ~ dnorm(grand.mean, .01)
    mu.strat[i] ~ dnorm(grand.mean, .01)
    
  }
   
  
}
  
  

```


```{r eval = F}

attobo.pilot.params <- c("diff", "mu.apt", "mu.eff", "mu.strat", "sigma")

```

```{r eval = F}



attobo.pilot.inits1 <-  list( "mu.apt" =  rep(grand.mean, 202),
                        "mu.eff" = rep(grand.mean, 202), 
                        "mu.strat" = rep(grand.mean, 202),
                        "sigma" = rep(1,202))
attobo.pilot.inits2 <- list( "mu.apt" =  rep(3.5, 202),
                        "mu.eff" = rep(3.5, 202), 
                        "mu.strat" = rep(3.5, 202),
                        "sigma" = rep(2,202))
attobo.pilot.inits3 <- list( "mu.apt" =  rep(5, 202),
                        "mu.eff" = rep(5, 202), 
                        "mu.strat" = rep(5, 202),
                        "sigma" = rep(3,202))
attobo.pilot.inits4 <- list( "mu.apt" =  rep(2.5, 202),
                        "mu.eff" = rep(2.5, 202), 
                        "mu.strat" = rep(2.5, 202),
                        "sigma" = rep(1,202))
attobo.pilot.inits5 <- list( "mu.apt" =  rep(6, 202),
                        "mu.eff" = rep(6, 202), 
                        "mu.strat" = rep(6, 202),
                        "sigma" = rep(5,202))

attobo.pilot.inits <- list(attobo.pilot.inits1, attobo.pilot.inits2,attobo.pilot.inits3, attobo.pilot.inits4,attobo.pilot.inits5)

```

```{r eval = F}

set.seed(1128)
attobo.pilot.fit <- jags(data = attobo.pilot.datjags, inits = attobo.pilot.inits, parameters.to.save = attobo.pilot.params, 
                n.chains = 5, n.iter = 100000, n.burnin = 10000, model.file = attobo.pilot.model)

attobo.pilot.fit.upd <- update(attobo.pilot.fit, n.iter =1000)
attobo.pilot.fit.upd <- autojags(attobo.pilot.fit)

```

```{r eval = FALSE}

attobo.pilot.fit.mcmc <- as.mcmc(attobo.pilot.fit)
save(attobo.pilot.fit.mcmc, file = "attobo.pilot.var.mcmc.RData")
summary(attobo.pilot.fit.mcmc)

```

### Convergence Diagnostics

```{r figure = TRUE, fig.width=6, fig.height=6, fig.align='center'}
                  
load("attobo.pilot.var.mcmc.RData")
                    
#  15 traces
MCMCtrace(attobo.pilot.fit.mcmc[,1:15], ind = TRUE, pdf = FALSE )

autocorr.plot(attobo.pilot.fit.mcmc[1][,1:15], ask = FALSE)

autocorr.plot(attobo.pilot.fit.mcmc[2][,1:15], ask = FALSE)

autocorr.plot(attobo.pilot.fit.mcmc[3][,1:15], ask = FALSE)

autocorr.plot(attobo.pilot.fit.mcmc[4][,1:15], ask = FALSE)

autocorr.plot(attobo.pilot.fit.mcmc[5][,1:15], ask = FALSE)
```

### Calculating quantiles
```{r eval = F}
attobo.pilot.var <- as.data.frame(as.matrix(attobo.pilot.fit.mcmc))
save(attobo.pilot.var, file = "attobo.pilot.var.RData")
```


```{r}
load("attobo.pilot.var.RData")

pred.diff <- attobo.pilot.var[, grep("diff[", colnames(attobo.pilot.var), fixed = T)]

## estimated difference for each participant
pred.diff <- pred.diff[, c(mixedsort(names(pred.diff)))]

diff.1 <- pred.diff[, 1:202]
diff.1$mean.1 <- apply(diff.1, 1, mean)

diff.2 <- pred.diff[, 203:404]
diff.2$mean.2 <- apply(diff.2, 1, mean)

diff.3 <- pred.diff[, 405:606]
diff.3$mean.3 <- apply(diff.3, 1, mean)

# no clear diff
quantile(diff.1$mean.1, probs = c(.025, .5, .975))
# no clear diff
quantile(diff.2$mean.2, probs = c(.025, .5, .975))
# no clear diff
quantile(diff.3$mean.3, probs = c(.025, .5, .975))

```


### Presenting Results

```{r echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
attobo.pilot.posterior.coefs <- cbind(diff.1$mean.1, diff.2$mean.2, diff.3$mean.3)
attobo.pilot.posterior.coefs <- as.data.frame(attobo.pilot.posterior.coefs)
names(attobo.pilot.posterior.coefs) <- c("Effort - Aptitude", "Strategy - Aptitude", "Strategy - Effort")

attobo.pilot.posterior.coefs.long <- gather(attobo.pilot.posterior.coefs)


```

```{r}

attobo.pilot.posterior.coefs.sum <- summarize(group_by(attobo.pilot.posterior.coefs.long, key),
                                        median_coef = median(value),
                                        lower_coef = quantile(value, probs = c(0.025)),
                                        upper_coef = quantile(value, probs = c(0.975)))
ggplot(data = attobo.pilot.posterior.coefs.sum, aes(x = median_coef, y = key)) + 
  geom_errorbarh(aes(xmin = lower_coef, xmax = upper_coef), height = 0.1) + 
  geom_point() + 
  geom_vline(xintercept = 0, linetype = "dashed") + 
  xlab("Posterior estimate") + ylab("") + 
  theme_bw()

```


## Uncontrollability

### Frequentist Estimates

```{r}

t.test(attobo.pilot$EffortUncon, attobo.pilot$AptUncon, paired = TRUE)

t.test(attobo.pilot$StratUncon, attobo.pilot$AptUncon,paired = TRUE)

t.test(attobo.pilot$StratUncon, attobo.pilot$EffortUncon, paired = TRUE)


```

### Bayesian Model - Uncontrollability

```{r eval = F}

apt.uncon <- attobo.pilot$AptUncon
eff.uncon <- attobo.pilot$EffortUncon
strat.uncon <- attobo.pilot$StratUncon

y <- c(apt.uncon, eff.uncon, strat.uncon)
grand.mean <- mean(y)

attobo.pilot.datjags <- list(apt.uncon = apt.uncon, eff.uncon = eff.uncon, strat.uncon = strat.uncon, N = nrow(attobo.pilot), grand.mean = grand.mean)
attobo.pilot.datjags
```

### Model Specification

```{r eval=F}

attobo.pilot.model <- function() {
  for(i in 1:N){
    # lambda is mean and variance of the poisson distribution
    
    apt.uncon[i] ~ dnorm(mu.apt[i], sigma[i]) # fixing error from each participant to be the same
    eff.uncon[i] ~ dnorm(mu.eff[i], sigma[i])
    strat.uncon[i] ~ dnorm(mu.strat[i], sigma[i])
    sigma[i] ~ dgamma(.01, .01) # all errors come from same distribution
  
    diff[1, i] <- mu.eff[i] - mu.apt[i]
    diff[2, i] <- mu.strat[i] - mu.apt[i]
    diff[3, i] <- mu.strat[i] - mu.eff[i]

    #priors
    mu.apt[i] ~ dnorm(grand.mean, .01)
    mu.eff[i] ~ dnorm(grand.mean, .01)
    mu.strat[i] ~ dnorm(grand.mean, .01)
    
  }
   
  
}
  
  

```


```{r eval = F}

attobo.pilot.params <- c("diff", "mu.apt", "mu.eff", "mu.strat", "sigma")

```

```{r eval = F}



attobo.pilot.inits1 <-  list( "mu.apt" =  rep(grand.mean, 202),
                        "mu.eff" = rep(grand.mean, 202), 
                        "mu.strat" = rep(grand.mean, 202),
                        "sigma" = rep(1,202))
attobo.pilot.inits2 <- list( "mu.apt" =  rep(3.5, 202),
                        "mu.eff" = rep(3.5, 202), 
                        "mu.strat" = rep(3.5, 202),
                        "sigma" = rep(2,202))
attobo.pilot.inits3 <- list( "mu.apt" =  rep(5, 202),
                        "mu.eff" = rep(5, 202), 
                        "mu.strat" = rep(5, 202),
                        "sigma" = rep(3,202))
attobo.pilot.inits4 <- list( "mu.apt" =  rep(2.5, 202),
                        "mu.eff" = rep(2.5, 202), 
                        "mu.strat" = rep(2.5, 202),
                        "sigma" = rep(1,202))
attobo.pilot.inits5 <- list( "mu.apt" =  rep(6, 202),
                        "mu.eff" = rep(6, 202), 
                        "mu.strat" = rep(6, 202),
                        "sigma" = rep(5,202))

attobo.pilot.inits <- list(attobo.pilot.inits1, attobo.pilot.inits2,attobo.pilot.inits3, attobo.pilot.inits4,attobo.pilot.inits5)

```

```{r eval = F}

set.seed(1128)
attobo.pilot.fit <- jags(data = attobo.pilot.datjags, inits = attobo.pilot.inits, parameters.to.save = attobo.pilot.params, 
                n.chains = 5, n.iter = 100000, n.burnin = 10000, model.file = attobo.pilot.model)

attobo.pilot.fit.upd <- update(attobo.pilot.fit, n.iter =1000)
attobo.pilot.fit.upd <- autojags(attobo.pilot.fit)

```

```{r eval = FALSE}

attobo.pilot.fit.mcmc <- as.mcmc(attobo.pilot.fit)
save(attobo.pilot.fit.mcmc, file = "attobo.pilot.uncon.mcmc.RData")
summary(attobo.pilot.fit.mcmc)

```

### Convergence Diagnostics

```{r figure = TRUE, fig.width=6, fig.height=6, fig.align='center'}

load("attobo.pilot.uncon.mcmc.RData")

#  15 traces
MCMCtrace(attobo.pilot.fit.mcmc[,1:15], ind = TRUE, pdf = FALSE )

autocorr.plot(attobo.pilot.fit.mcmc[1][,1:15], ask = FALSE)

autocorr.plot(attobo.pilot.fit.mcmc[2][,1:15], ask = FALSE)

autocorr.plot(attobo.pilot.fit.mcmc[3][,1:15], ask = FALSE)

autocorr.plot(attobo.pilot.fit.mcmc[4][,1:15], ask = FALSE)

autocorr.plot(attobo.pilot.fit.mcmc[5][,1:15], ask = FALSE)
```

### Calculating quantiles
```{r eval = F}
attobo.pilot.uncon <- as.data.frame(as.matrix(attobo.pilot.fit.mcmc))
save(attobo.pilot.uncon, file = "attobo.pilot.uncon.RData")
```

```{r}
load("attobo.pilot.uncon.RData")

pred.diff <- attobo.pilot.uncon[, grep("diff[", colnames(attobo.pilot.uncon), fixed = T)]

## estimated difference for each participant
pred.diff <- pred.diff[, c(mixedsort(names(pred.diff)))]

diff.1 <- pred.diff[, 1:202]
diff.1$mean.1 <- apply(diff.1, 1, mean)

diff.2 <- pred.diff[, 203:404]
diff.2$mean.2 <- apply(diff.2, 1, mean)

diff.3 <- pred.diff[, 405:606]
diff.3$mean.3 <- apply(diff.3, 1, mean)

# no clear diff
quantile(diff.1$mean.1, probs = c(.025, .5, .975))
# no clear diff
quantile(diff.2$mean.2, probs = c(.025, .5, .975))
# no clear diff
quantile(diff.3$mean.3, probs = c(.025, .5, .975))

```


### Presenting Results

```{r echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
attobo.pilot.posterior.coefs <- cbind(diff.1$mean.1, diff.2$mean.2, diff.3$mean.3)
attobo.pilot.posterior.coefs <- as.data.frame(attobo.pilot.posterior.coefs)
names(attobo.pilot.posterior.coefs) <- c("Effort - Aptitude", "Strategy - Aptitude", "Strategy - Effort")

attobo.pilot.posterior.coefs.long <- gather(attobo.pilot.posterior.coefs)

```

```{r}

attobo.pilot.posterior.coefs.sum <- summarize(group_by(attobo.pilot.posterior.coefs.long, key),
                                        median_coef = median(value),
                                        lower_coef = quantile(value, probs = c(0.025)),
                                        upper_coef = quantile(value, probs = c(0.975)))
ggplot(data = attobo.pilot.posterior.coefs.sum, aes(x = median_coef, y = key)) + 
  geom_errorbarh(aes(xmin = lower_coef, xmax = upper_coef), height = 0.1) + 
  geom_point() + 
  geom_vline(xintercept = 0, linetype = "dashed") + 
  xlab("Posterior estimate") + ylab("") + 
  theme_bw()

```
