---
title: "Study 2 Analysis (Academic Domain)"
author: "Dennis W.H. Teo"
output: 
  html_document:
    theme: darkly
    toc: yes
    toc_depth: 3
    toc_float: true
    highlight: tango
    df_print: paged
    fig_caption: false
    code_fold: hide
fontsize: 18pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

```{r results='hide', warning=F, message=F}

library(psych)
library(ggplot2)
library(tidyverse)
library(effects)
## Library for the multiple comparisons
library(phia)
## Library to compute the effect sizes
library(sjstats)
library(lsr)
library(lavaan)
library(ggthemes)
library(tibble)
library(car)
library(olsrr)
library(pwr)
library(dthelper)
library(glm2)
library(betareg)
library(readr)
select <- dplyr::select

reverse.logodds <- function(x){
  exp(x)/(1+exp(x))
}

report <- function(x,dp=2){
  m <- round(mean(x, na.rm=T),dp)
  s <- round(sd(x, na.rm=T),dp)
  return(paste0(m, " (", s, ")"))
}
```

```{r}
# loading and wrangling data

attobo <- read_csv("attobo2_clean.csv")

colnames(attobo) <- tolower(colnames(attobo))

attobo$scenario <- as.factor(attobo$scenario)

attobo$attribution <- attobo$scenario

attobo$attribution_effort <- factor(attobo$attribution, levels = c("Effort", "Strategy", "Aptitude"))
attobo$attribution_strat <- factor(attobo$attribution, levels = c( "Strategy","Effort", "Aptitude"))

attobo$expectancy <- (attobo$expectancy - 1)/10
attobo$expectancy <- ifelse(attobo$expectancy == 1, .999,
                     ifelse(attobo$expectancy == 0, .001, attobo$expectancy) )

attobo <- attobo %>%
  rename(selfdirected = combined_method,
         workharder = bruteforce,
         mandatory = convergent_method 
         )

attobo.advice <- attobo %>%
  select(selfdirected, workharder, seekhelp, mandatory,
         total, expectancy)

attobo.attribution <- attobo %>%
  select(aptout, aptvar, aptuncon, 
         effortout, effortvar, effortuncon,
         stratout, stratvar, stratuncon,
         luckout, luckvar, luckuncon,
         taskout, taskvar, taskuncon,
         moodout, moodvar, mooduncon)

attobo.others <- attobo %>%
  select(expectancy, gender, age, education, sms_mean,
         smo_mean, mp_mean, so_mean)


```

# Descriptive Stats

## Sample Breakdown

```{r}
## Sample Breakdown
attobo %>%
  mutate(`Attibution Condition` = attribution) %>%
  group_by(`Attibution Condition`) %>%
  summarise(N = n())
```

## Descriptives of Advice Counts by Experimental Condition

Note: Originally, the coders counted each advice type. Subsequently, these counts were converted to presence/absence to make the results more comparable to the previous study. The descriptive stats below show the mean and sd (in brackets) of the counts of each advice type by attribution condition.

```{r}
attobo %>%
  mutate(`Attibution Condition` = attribution) %>%
  group_by(`Attibution Condition`) %>%
  summarise(
    `Self-directed` = report(selfdirected),
    `Work Harder` = report(workharder),
    `Mandatory` = report(mandatory)
  )
```
## Histograms of Collected Measures

```{r }

ggplot(data = gather(attobo.advice, factor_key = TRUE), aes(x = factor(value))) +
  geom_bar() + 
  facet_wrap(~ key,scales = "free", as.table = TRUE, nrow = 3) + xlab("") + 
  theme_bw()

ggplot(data = gather(attobo.attribution, factor_key = TRUE), aes(x = factor(value))) +
  geom_bar() + 
  facet_wrap(~ key,scales = "free", as.table = TRUE, nrow = 3) + xlab("") + 
  theme_bw()

ggplot(data = gather(attobo.others, factor_key = TRUE), aes(x = factor(value))) +
  geom_bar() + 
  facet_wrap(~ key,scales = "free", as.table = TRUE, nrow = 3) + xlab("") + 
  theme_bw()

```

# Main Analysis
## Work Harder Study Methods {.tabset}

### Model and Hypothesis test

```{r}
attobo$workharder_bool <- ifelse(attobo$workharder > 0, 1, 0)

workharder.model<- glm2(workharder_bool ~ attribution_effort, data = attobo, family = binomial(link = "logit"))

summary(workharder.model)
confint(workharder.model)
Anova(workharder.model)

# compute effect size
model.anova <- car::Anova(workharder.model)
cohen.w <- sqrt(model.anova$`LR Chisq`[1]/(1*nrow(attobo)))
print(paste("Cohen W:", round(cohen.w,3) ))

```

### Converted Estimates (to probability)

```{r}

workharder.coefs <- summary(workharder.model)$coefficients

workharder.summary <- data.frame(
  advice = rep("Work Harder",3),
  attribution = c("Effort", "Strategy","Aptitude"),
  mean = c(reverse.logodds(workharder.coefs[1, "Estimate"]), reverse.logodds(workharder.coefs[1, "Estimate"] + workharder.coefs[2, "Estimate"]), reverse.logodds(workharder.coefs[1, "Estimate"] + workharder.coefs[3, "Estimate"])),
  lower = c(reverse.logodds(confint(workharder.model)[1,])[1], reverse.logodds(workharder.coefs[1, "Estimate"] + confint(workharder.model)[2,])[1], reverse.logodds(workharder.coefs[1, "Estimate"] + confint(workharder.model)[3,])[1]),
  upper = c(reverse.logodds(confint(workharder.model)[1,])[2], reverse.logodds(workharder.coefs[1, "Estimate"] + confint(workharder.model)[2,])[2], reverse.logodds(workharder.coefs[1, "Estimate"] + confint(workharder.model)[3,])[2])
)

coef.summary <- workharder.summary

colnames(workharder.summary) <- c("Advice", "Attribution", "Mean", "Lower", "Upper")
workharder.summary
```

## Mandatory Study Methods {.tabset}

### Model and Hypothesis test

```{r}

attobo$mandatory_bool <- ifelse(attobo$mandatory > 0, 1, 0)

mandatory.model <- glm2(mandatory_bool ~ attribution_effort, data = attobo, family = binomial(link = "logit"))

summary(mandatory.model)
confint(mandatory.model)
Anova(mandatory.model)

# compute effect size
model.anova <- car::Anova(mandatory.model)
cohen.w <- sqrt(model.anova$`LR Chisq`[1]/(1*nrow(attobo)))
print(paste("Cohen W:", round(cohen.w,3) ))

```
### Converted Estimates (to probability)

```{r}

mandatory.coefs <- summary(mandatory.model)$coefficients

mandatory.summary <- data.frame(
  advice = rep("Mandatory",3),
  attribution = c("Effort", "Strategy","Aptitude"),
  mean = c(reverse.logodds(mandatory.coefs[1, "Estimate"]), reverse.logodds(mandatory.coefs[1, "Estimate"] + mandatory.coefs[2, "Estimate"]), reverse.logodds(mandatory.coefs[1, "Estimate"] + mandatory.coefs[3, "Estimate"])),
  lower = c(reverse.logodds(confint(mandatory.model)[1,])[1], reverse.logodds(mandatory.coefs[1, "Estimate"] + confint(mandatory.model)[2,])[1], reverse.logodds(mandatory.coefs[1, "Estimate"] + confint(mandatory.model)[3,])[1]),
  upper = c(reverse.logodds(confint(mandatory.model)[1,])[2], reverse.logodds(mandatory.coefs[1, "Estimate"] + confint(mandatory.model)[2,])[2], reverse.logodds(mandatory.coefs[1, "Estimate"] + confint(mandatory.model)[3,])[2])
)

coef.summary <- rbind(coef.summary,mandatory.summary)

colnames(mandatory.summary) <- c("Advice", "Attribution", "Mean", "Lower", "Upper")
mandatory.summary

```


## Self-directed Study Methods {.tabset}

### Model and Hypothesis test

```{r}

attobo$selfdirected_bool <- ifelse(attobo$selfdirected > 0, 1, 0)

selfdirected.model<- glm2(selfdirected_bool ~ attribution_strat, data = attobo, family = binomial(link = "logit"))

summary(selfdirected.model)
confint(selfdirected.model)
Anova(selfdirected.model)

# compute effect size
model.anova <- car::Anova(selfdirected.model)
cohen.w <- sqrt(model.anova$`LR Chisq`[1]/(1*nrow(attobo)))
print(paste("Cohen W:", round(cohen.w,3) ))

```
### Converted Estimates (to probability)

```{r}
selfdirected.coefs <- summary(selfdirected.model)$coefficients

selfdirected.summary <- data.frame(
  advice = rep("Self-Directed",3),
  attribution = c("Strategy", "Effort","Aptitude"),
  mean = c(reverse.logodds(selfdirected.coefs[1, "Estimate"]), reverse.logodds(selfdirected.coefs[1, "Estimate"] + selfdirected.coefs[2, "Estimate"]), reverse.logodds(selfdirected.coefs[1, "Estimate"] + selfdirected.coefs[3, "Estimate"])),
  lower = c(reverse.logodds(confint(selfdirected.model)[1,])[1], reverse.logodds(selfdirected.coefs[1, "Estimate"] + confint(selfdirected.model)[2,])[1], reverse.logodds(selfdirected.coefs[1, "Estimate"] + confint(selfdirected.model)[3,])[1]),
  upper = c(reverse.logodds(confint(selfdirected.model)[1,])[2], reverse.logodds(selfdirected.coefs[1, "Estimate"] + confint(selfdirected.model)[2,])[2], reverse.logodds(selfdirected.coefs[1, "Estimate"] + confint(selfdirected.model)[3,])[2])
)

coef.summary <- rbind(coef.summary, selfdirected.summary)

colnames(selfdirected.summary) <- c("Advice", "Attribution", "Mean", "Lower", "Upper")
selfdirected.summary

```

## Expectancy {.tabset}

### Model and Hypothesis test

```{r}

expectancy.model<- betareg(expectancy ~ attribution, data = attobo, link = "logit" )

summary(expectancy.model)
confint(expectancy.model)
Anova(expectancy.model)

```

### Converted Estimates (to probability)

```{r}
expectancy.coefs <- summary(expectancy.model)$coefficients$mean

expectancy.summary <- data.frame(
  attribution = c("Effort", "Strategy","Aptitude"),
  mean = c(reverse.logodds(expectancy.coefs[1, "Estimate"] + expectancy.coefs[2, "Estimate"]), reverse.logodds(expectancy.coefs[1, "Estimate"] + expectancy.coefs[3, "Estimate"]), reverse.logodds(expectancy.coefs[1, "Estimate"])),
  lower = c(reverse.logodds(expectancy.coefs[1, "Estimate"] + confint(expectancy.model)[2,])[1], reverse.logodds(expectancy.coefs[1, "Estimate"] + confint(expectancy.model)[3,])[1], reverse.logodds(confint(expectancy.model)[1,])[1]),
  upper = c(reverse.logodds(expectancy.coefs[1, "Estimate"] + confint(expectancy.model)[2,])[2], reverse.logodds(expectancy.coefs[1, "Estimate"] + confint(expectancy.model)[3,])[2], reverse.logodds(confint(expectancy.model)[1,])[2])
)
colnames(expectancy.summary) <- c("Attribution", "Mean", "Lower", "Upper")
expectancy.summary
```



## Rely-on-others Study Advice (Exploratory) {.tabset}

```{r}
attobo$seekhelp_bool <- ifelse(attobo$seekhelp > 0, 1, 0)

seekhelp.model<- glm2(seekhelp_bool ~ attribution, data = attobo, family = binomial(link = "logit"))

summary(seekhelp.model)
confint(seekhelp.model)
Anova(seekhelp.model)

# compute effect size
model.anova <- car::Anova(seekhelp.model)
cohen.w <- sqrt(model.anova$`LR Chisq`[1]/(1*nrow(attobo)))
print(paste("Cohen W:", round(cohen.w,3) ))

```

### Converted Estimates (to probability)

```{r}

seekhelp.coefs <- summary(seekhelp.model)$coefficients

seekhelp.summary <- data.frame(
  advice = rep("Rely on others Study Advice",3),
  attribution = c("Aptitude", "Effort", "Strategy"),
  mean = c(reverse.logodds(seekhelp.coefs[1, "Estimate"]), reverse.logodds(seekhelp.coefs[1, "Estimate"] + seekhelp.coefs[2, "Estimate"]), reverse.logodds(seekhelp.coefs[1, "Estimate"] + seekhelp.coefs[3, "Estimate"])),
  lower = c(reverse.logodds(confint(seekhelp.model)[1,])[1], reverse.logodds(seekhelp.coefs[1, "Estimate"] + confint(seekhelp.model)[2,])[1], reverse.logodds(seekhelp.coefs[1, "Estimate"] + confint(seekhelp.model)[3,])[1]),
  upper = c(reverse.logodds(confint(seekhelp.model)[1,])[2], reverse.logodds(seekhelp.coefs[1, "Estimate"] + confint(seekhelp.model)[2,])[2], reverse.logodds(seekhelp.coefs[1, "Estimate"] + confint(seekhelp.model)[3,])[2])
)

colnames(seekhelp.summary) <- c("Advice", "Attribution", "Mean", "Lower", "Upper")
seekhelp.summary

```

# Graphs

```{r}


coef.summary$Advice <- factor(coef.summary$advice, levels = c("Work Harder", "Mandatory", "Self-Directed"))

coef.summary$Attribution <- factor(coef.summary$attribution, levels = c( "Effort", "Strategy", "Aptitude" ))

colnames(coef.summary) <- c("Advice", "Attribution", "Mean", "Lower", "Upper")
coef.summary
```

```{r}


attobo1.advice.plot <-  ggplot(coef.summary, aes(x = Attribution, y = Mean, shape = Advice)) + 
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                 position=position_dodge(.5))+
  geom_point(aes(col = Advice), position=position_dodge(.5), size = 3) +
  scale_color_manual(values = c("#D55E00", "#009E73", "#0072B2")) +
  scale_shape_manual(values = c(16 , 15,17)) +
  ylab("Probability of Advice") + xlab("") + 
  theme_bw() +
  theme(text = element_text(size = 18),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) 

attobo1.advice.plot
```






